---
title: "Cabbages"
author: "Jennifer Nava"
date: "June 13, 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The method's that I will be using are ggplot, numerical descriptive comparisons, and inferential results. I will use these descriptors to compare variables and see what cultivation method is producing more Vitamin C. I will also use Inferential Results to either reject or accept the null hypothesis. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

It seems that there is more Vitamin C on cultivation method c52 than c39.   
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```


It appears that there is more vitamin C in C52 with he average of 64.4 and the average of C39 is 51.5.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

It seems that the difference in p-values are small, therefor I will reject the null hypothesis


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In conclusion, the ggplot box graph demonstrated a higher amount of Vitamin C in cult C52 than C39. The numerical descriptive results exhibited a higher average in Vitamin C on cultivation method C52. Finally, the t-test results displayed a small p-value, this made me reject the null hypothesis. The answer to the initial question, is there a difference in average Vitamin C between Cult C52 and C39? The answer is yes, there is a difference due to C52 containing a higher amount of Vitamin C. 